### 2019-05-26 report/chapter04.Rnw
Präsentation
Presentation update
After presentation update

@@

\begin{align}
y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
\end{align}

>>>>

\section{Transformation between effect sizes}
Binary and continuous outcome measures can both be transformed into correlations and fishers z-scaled correlations in order to be compared. Let $\theta$ be a log odds ratio. A standardized mean difference $d$ (also known as Cohen's $d$) is calculated by multiplying $\theta$ with $\sqrt{3}/\pi$. The variance of the standardized mean difference is attained as $v_d = v_\theta \sqrt{3}/\pi$.\\
We get from a standardized mean difference $d$ to a correlation $r$ by using 
\begin{align}
r &= \frac{d}{\sqrt{d^2 + a}} \nonumber
\end{align}
where $a$ is a correction factor if $n_t \neq n_c, a = (n_c + n_t)^2 / n_c n_t$. The variance of $r$ is computed by using 
\begin{align}
v_r &= v_d
\end{align}

Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $v_z$ by using
\begin{align}
z &= 0.5 \ln(\frac{1 + r}{1 - r}) \nonumber
v_z &= \frac{1}{n-3}
\end{align}

@@

\begin{align}
y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{v_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
\end{align}
